Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-15 paper.tex
remove old paragraph
rework uncertainty measurement description

\section{Results}
In this specific study, one will only focus on the uncertainty on the produced
electric power as a function of time, on the total quantity of natural uranium
used and on the total unused fissile inventory (unused reprocessed plutonium).
In order to estimate the total uncertainty on those 3 parameters as well as the
individual contribution of the operational parameters several set of (199)
simulations have been completed.  All uncertainty are computed as the standard
deviation over over all the calculations in the set.

In addition to the set with all parameters are sampled according to their
uncertainty, a set a have been computed for each parameter, with all the other
remaining fixed to the reference value.

\subsection{Generated Power}
By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
generated power is expected.

@@

Those time related parameters can not only impact the uncertainty as
physical parameters (for example the cycle length impacting the fuel discharge
burnup and composition)

>>>>

\section{Results}

As nuclear archaeology main interests are high enrich uranium production and
fissile inventories, this specific study will mainly focus on the uncertainty on
the total quantity of natural uranium used and on the total unused fissile
inventory (unused reprocessed plutonium).

Generated power will briefly being investigated to ensure the overall
uncertainty study will not be contaminated with fuel miss loading, which could
be interesting but are not the focus on this work.

For this study 6 set of 199 simulations, and a reference calculation have been
computed: One for each of the 5 uncertain parameters, one varying parameter the
4 others remaining fix, one with all 5 parameters varying and one single
simulation where all the 5 parameters were fixed at the mean value.

All uncertainty have been computed as the standard deviation over over all the
calculations in a single set.

\subsection{Generated Power}

By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
generated power is expected.

@@
